Inferring Invariants of Distributed Programs

### 2015-04-03 Doc/introback.tex
some typos

\section{Motivating Example}
For motivation example, consider sudo-two-phase-commit protocol of figure \ref{lst:2pc}. In this protocol coordinator first queries other nodes for their vote and if all nodes including the coordinator vote ``Commit" then coordinator sends ``Commit", otherwise it sends ``Abort" to all other nodes. At the end of this protocol all nodes should either commit or abort . In order to verify that this algorithm is working correctly, developers can examine inferred invariants of the protocol execution and inspect if these inferred invariants match expected behaviour of the system (In this case commit value of all nodes should have the same value and this property should be inferred by executing the protocol). We use daikon \cite{ernst2001dynamically} to infer invariants between variables so we can infer linear ($y = ax + b$), ordering ($y < x$) and containment ($x \in y$) relationships that may hold between the distributed state variables of all nodes in the system.

\begin{figure}
\centering
\begin{lstlisting}[caption={Coordinator Code}]
for i := 1 to n do
	send('Q',i)
commit := decide()
for i:= 1 to n do
	recv(buf,i)
	if (buf == 'A')
		commit := 'A'
for i := 1 to n
	send(commit, i)
\end{lstlisting}
\begin{lstlisting}[caption={Coordinator Code}]
recv(buf)
if(buf == 'Q')
	vote:= decide()
	send(vote)
if (vote == 'A')
	commit = 'A'
else
	recv(buf)
	commit = buf
\end{lstlisting}
\caption{Sudo two phase commit code for coordinator and cohorts}
\label{lst:2pc}
\end{figure}

>>>>

\section{Motivating Example}
For motivation example, consider pseudo-two-phase-commit protocol of figure \ref{lst:2pc}. In this protocol coordinator first queries other nodes for their vote and if all nodes including the coordinator vote ``Commit" then coordinator sends ``Commit", otherwise it sends ``Abort" to all other nodes. At the end of this protocol all nodes should either commit or abort . In order to verify that this algorithm is working correctly, developers can examine inferred invariants of the protocol execution and inspect if these inferred invariants match expected behaviour of the system (In this case commit value of all nodes should have the same value and this property should be inferred by executing the protocol). We use daikon \cite{ernst2001dynamically} to infer invariants between variables so we can infer linear ($y = ax + b$), ordering ($y < x$) and containment ($x \in y$) relationships that may hold between the distributed state variables of all nodes in the system.

\begin{figure}
\centering
\begin{lstlisting}[caption={Coordinator Code}]
for i := 1 to n do
	send('Q',i)
commit := decide()
for i:= 1 to n do
	recv(buf,i)
	if (buf == 'A')
		commit := 'A'
for i := 1 to n
	send(commit, i)
\end{lstlisting}
\begin{lstlisting}[caption={Coordinator Code}]
recv(buf)
if(buf == 'Q')
	vote:= decide()
	send(vote)
if (vote == 'A')
	commit = 'A'
else
	recv(buf)
	commit = buf
\end{lstlisting}
\caption{Pseudo two phase commit code for coordinator and cohorts}
\label{lst:2pc}
\end{figure}
